---
title: "Homework1"
Author: Hanran Wei
output: Github_document
---

This is my solution to homework1

```{r}
library(tidyverse)
```


##Problem 1

Create a dataframe with specified elements

```{r}
prob1_df =
  tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  char_vec = c("a","b","c","d","e","f","g","h","i","j"),
  factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
)

```

Take mean of each variable

```{r}
mean(pull(prob1_df,samp))
mean(pull(prob1_df,samp_gt_0))
mean(pull(prob1_df,char_vec))
mean(pull(prob1_df,factor_vec))
```
I can take mean of numbers and logical but not char or factor

```{r}
as.numeric(pull(prob1_df,samp))
as.numeric(pull(prob1_df,samp_gt_0))
as.numeric(pull(prob1_df,char_vec))
as.numeric(pull(prob1_df,factor_vec))
```

```{r}
as.numeric(pull(prob1_df,samp_gt_0)) * pull(prob1_df,samp)
as.factor(pull(prob1_df,samp_gt_0)) * pull(prob1_df,samp)
as.numeric(as.factor(pull(prob1_df,samp_gt_0))) * pull(prob1_df,samp)
```



##Problem 2

Description of dataset

The dataset penguins includes the species, island, bill_length_mm, bill_depth_mm
flipper_length_mm, body_mass_g, sex, year.

Some important value:
The largest flipper length is 231 mm
The max body mass is 6300g and the min body mass is 2700g
52 peguins from Torgersen island
Adelie species is the largest specie with 152 penguins

The dataset consists 344 rows and 8 columns

The mean flipper length is 200.967 mm
```{r}
data("penguins", package = "palmerpenguins")
print(penguins)
c(nrow(penguins),ncol(penguins))
summary(penguins)
```

Make Scatterplot

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("hw1_scatter.pdf", height = 4, width = 4)
```


